A hazards approach to the biometric analysis of infant mortality

### 2023-03-13 Slides/slides.Rmd
Updates

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.width = 11, warning = FALSE, comment = NA)

@@

@@

## Study area 1: Västerbotten 1861--1950

\includegraphics[width=0.8\textwidth]{myfigs/vb.png}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.width = 9, warning = FALSE, comment = NA)

@@

## The log-cube transform

\begin{columns}
\begin{column}{0.6\textwidth}
\begin{equation*}
g(t) = C \log^3(t + 1), \; 0 < t \le 365.
\end{equation*}

where $C$ is a normalizing constant:

\begin{equation*}
C = \frac{365}{\log^3(365 + 1)}
\end{equation*}
\end{column}

\begin{column}{0.5\textwidth}
\includegraphics[width=0.9\textwidth]{../paper2_files/figure-latex/logcube-1.pdf}
\end{column}

\end{columns}

@@

## Study areas

\begin{columns}
\begin{column}{0.5\textwidth}
\begin{center}
Skåne 1711--1800

\includegraphics[width=0.7\textwidth]{myfigs/scania.png}
\end{center}
\end{column}
\begin{column}{0.5\textwidth}
\begin{center}
Västerbotten 1801--1950

\includegraphics[width=0.8\textwidth]{myfigs/vb.png}
\end{center}
\end{column}
\end{columns}
